### 2022-10-15 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@c15bddd0648f41e9bd3fbfdd2cd45cbc6bf5b682 🚀

\textbf{Correspondance to:}\\
Michael D. Catchen --- \texttt{michael.catchen@mail.mcgill.ca}\\

@@

Species interactions drive many processes in evolutionary biology and
community ecology. A better understanding of interactions among species
is an imperative to both mitigate the potentially harmful impacts of
anthropogenic change on Earth's biodiversity (Makiola \emph{et al.}
2020) and to predict zoonotic spillover of disease to prevent future
pandemics (Becker \emph{et al.} 2021). However, meeting these challenges
is difficult because interactions are intrinsically hard to sample
(Jordano 2016). Over the past few decades biodiversity data has become
increasingly available--for example, remote-sensing has enabled
collection of data on spatial scales and resolutions previously
unimaginable, and improved in-situ sensing (Stephenson 2020), while the
adoption of open data practices (Kenall \emph{et al.} 2014) have
substantially increased the amount of data available to ecologists.
Still, widespread data about species interactions remains elusive
(Poisot \emph{et al.} 2021). Observing an interaction between two
species often requires human observation because remote sampling methods
can primarily detect co-occurrence (Niedballa \emph{et al.} 2019), and
this itself is not necessarily indicative of an interaction (Blanchet
\emph{et al.} 2020). This constraint induces biases on species
interaction data subject to the spatial and temporal scales that current
observation methods can feasibly sample. This is further compounded by
semantic confusion around the word ``interaction''---for example one
could consider competition a form of species interaction, even though
this is marked by a lack of co-occurrence between species, unlike other
types of interactions, like trophism or pollination, which require both
species to be together at the same place and time. Here we define
interaction in the latter sense, where two species have fitness
consequences on one-another if they are in the sample place at the same
time. Further we only consider direct (not higher-order) interactions.

The importance of sampling effort and its impact on resulting ecological
data has produced a rich body of literature. The recorded number of
species in a dataset or sample depends on the total number of
observations (Walther \emph{et al.} 1995; Willott 2001)---as do
estimates of population abundance (Griffiths 1998)---in addition to
spatial coverage and species detectability. This has motivated more
quantitatively robust approaches to account for error in sampling data
in many contexts: to determine if a given species is extinct (Boakes
\emph{et al.} 2015), to determine sampling design (Moore \& McCarthy
2016),and to measure species richness across large scales (Carlson
\emph{et al.} 2020). In the context of interactions, an initial concern
was the compounding effects of limited sampling effort combined with the
amalgamation of data (across both study sites, time of year, and
taxonomic scales) could lead any empirical set of observations to
inadequately reflect the reality of how species interact
{[}Paine1988RoaMap{]} or the structure of the network as a whole
{[}McLeod2021SamAsy{]}. Martinez \emph{et al.} (1999) showed that in a
plant-endophyte trophic network, network connectance is robust to
sampling effort, but this was done in the context of a system for which
observation of 62,000 total interactions derived from 164,000
plant-stems was feasible. In some systems (e.g.~megafauna food-webs)
this many observations is either impractical or infeasible due to the
absolute abundance of the species in question.

We cannot feasibly observe all (or even most) of the direct interactions
that occur in an ecosystem. This means we can be confident two species
actually interact if we have a record of it (given an estimate of
species misidentification probability), but not at all confident that a
pair of species do not interact if we have no record of those species
observed together. In other words, it is difficult to distinguish
true-negatives (two species never interact) from false-negatives (two
species interact in some capacity, but we do not have a record of it).
For a concrete example of this phenomenon, see Figure Concept. Because
even the most highly sampled systems will still contain missing
interactions, there is increasing interest in combining species-level
data (e.g. traits, abundance, range, phylogenetic relatedness, etc.) to
build predictive models of interactions (Strydom \emph{et al.} 2021).
However, the noise of false-negatives could impact the efficacy of our
predictive models and have practical consequences for answering
questions about interactions (de Aguiar \emph{et al.} 2019). This data
constraint is amplified as the interaction data we have is
geographically biased toward the usual suspects (Poisot \emph{et al.}
2021). We therefore need a systematic approach to assessing these biases
in the observation process and the consequences this has for our
understanding of interaction networks

The intrinsic properties of ecological communities create several
challenges for sampling: first, species are not observed with equal
probability---we are much more likely to observe a species of high
abundance than one of very low abundance (Poisot \emph{et al.} 2015).
Canard \emph{et al.} (2012) presents a null model of food-web structure
where species encounter one-another directly in proportion to each
species' relative-abundance. This assumes that there are no associations
in species co-occurrence due to an interaction (perhaps because this
interaction is ``important'' for both species; Cazelles \emph{et al.}
(2016)), but in this paper we later show increasing strength of
associations leads to increasing probability of false-negatives in
interaction data, and that these positive associations are rampant in
existing network data. Second, observed co-occurrence is often equated
with meaningful interaction strength, but this is not necessarily the
case Blanchet \emph{et al.} (2020)---a true ``non-interaction'' would
require that neither of two species, regardless of whether they
co-occur, exhibit any meaningful effect on the fitness of the other. So,
although co-occurrence is not directly indicative of an interaction, it
is a precondition for interactions, and therefore observations of
``non-interactions'' between pairs of species that are outside of the
union of both species ranges do not provide any information about that
interaction, i.e.~they should be excluded from consideration.

Here, we illustrate how our confidence that a pair of species we believe
to not interact highly depends on sampling effort, and suggest that
surveys of species interactions can benefit from simulation modeling of
detection probability. We demonstrate that the realized false-negative
rate of interactions is directly related to the relative abundance of
the species involved, and demonstrate how simulation can be used to
produce a null estimate of the false-negative rate as a function of
total sampling effort (the total count of all individuals of all species
seen). We show that positive associations in co-occurrence data can
increase realized probability of false negatives, and demonstrate these
positive associations are ubiquitous in network datasets. We conclude by
recommending that the simulation of sampling effort and species
occurrence can and should be used to help design surveys of species
interaction diversity (Moore \& McCarthy 2016), and by advocating use of
null models like those presented here as a tool for both guiding design
of surveys of species interactions and for modeling detection error in
predictive models.

@@

We start with a naive model of interaction detection: we assume that
every interacting pair of species is incorrectly observed as a
not-interacting with an independent and fixed probability, which we
denote pfn and subsequently refer to as the False-Negative Rate (FNR).
If we observe the same species not-interacting N times, then the
probability of a true-negative (denoted \(p_{tn}\)) is given by
\(p_{tn}=1-(p_{fn})^N\). This relation (the probability-mass-function of
geometric distribution, a special case of the negative-binomial
distribution) is shown in Figure 1(A) for varying values of \(p_{fn}\)
and illustrates a fundamental link between our ability to reliably say
an interaction doesn't exist---\(p_{tn}\)---and the number of times we
have observed a given species. In addition, note that also there is no
non-zero \(p_{fn}\) for which we can ever prove that an interaction does
not exist---no matter how many observations of non-interactions \(N\) we
have, \(p_{tn}<1\).

From Figure 1(A) it is clear that the more often we see two species
co-occurring, but not interacting, the more likely the interaction is a
true negative. This has several practical consequences: first it means
negatives taken outside the overlap of the range of each species aren't
informative. Second, we can use this relation to compute the expected
number of total observations needed to obtain a ``goal'' number of
observations of a particular pair of species (Figure 1(B)). As an
example, if we hypothesize that \(A\) and \(B\) do not interact, and we
want to see species \(A\) and \(B\) both co-occurring and not
interacting 10 times to be confident this is a true negative, then we
need an expected 1000 observations of all species if the relative
abundances of \(A\) and \(B\) are both \(0.1\).

@@

We now show that the realized false-negative rate of species
interactions changes drastically with sampling effort due to the
intrinsic variation of the abundance of individuals of each species
within a community. We do this by simulating the process of observation
of species interactions, applied both to 243 empirical food webs from
the Mangal database (Banville \emph{et al.} 2021) as well as random
food-webs generated using the niche model (Williams \& Martinez 2000), a
simple generative model of food-web structure. Our neutral model of
observation assumes each observed species is drawn from the distribution
in proportion to each species' abundance at that place and time.

The abundance distribution of a community can be reasonably-well
described by a log-normal distribution (Volkov \emph{et al.} 2003). In
addition to the log-normal distribution, we also tested the case where
the abundance distribution is derived from power-law scaling
\(Z^{(log(T_i)-1)}\) where \(T_i\) is the trophic level of species \(i\)
and \(Z\) is a scaling coefficient (Savage \emph{et al.} 2004), which
yields the same qualitative behavior. The practical consequence of
abundance distributions spanning many orders of magnitude of abundance
is that observing two ``rare'' species interacting requires two low
probability events: observing two rare species at the same time.

@@

where the MAP estimate of \((\mu, \phi)\) applied to Mangal data from
{[}{]} MacDonald et al.~2020 is \((\mu=0.086, \phi=24.3)\). All
simulations were done with 500 independent replicates per unique number
of observations n.~All analyses presented here are done in Julia v1.8
(Bezanson \emph{et al.} 2015) using both EcologicalNetworks.jl v0.5 and
Mangal.jl v0.4 (Banville \emph{et al.} 2021) and are hosted at
(GITHUB\_LINK\_TODO). Note that the empirical data, for the reasons
described above, very likely already contains many false negatives,
we'll revisit this issue in the final section.

From fig.~\ref{fig:geometric}(C) it is evident that the number of
species considered in a study is inseparable from the false-negative
rate in that study, and this effect should be taken into account when
designing samples of ecological networks in the future. We see a similar
qualitative pattern in fig.~\ref{fig:geometric}(D) where the FNR drops
off quickly as a function of observation effort, mediated by total
richness. The practical consequence of the bottom row of Figure 1 is
whether the total number of observations of all species (the x-axis) for
the range of possible FNR we deem acceptable (the y-axis) is feasible.
This raises two points: first, empirical data on interactions are
subject to the practical limitations of funding and human-work hours,
and therefore existing data tend to fall on the order of hundreds or
thousands observations of individuals per site. Clear aggregation of
data on sampling effort has proven difficult to find and a meta-analysis
of network data and sampling effort seems both pertinent and necessary,
in addition to the effects of aggregation of interactions across
taxonomic scales (Gauzens \emph{et al.} 2013; Giacomuzzo \& Jordán
2021). This inherent limitation on in-situ sampling means we should
optimize where we sample across space so that for a given number of
samples, we obtain the maximum information possible. Second, what is
meant by ``acceptable'' FNR? This raises the question: does a shifting
FNR lead to rapid transitions in the our ability inference and
predictions about the structure and dynamics of networks, or does it
produce a roughly linear decay in model efficacy? We explore this in the
next section.

@@

This model above doesn't consider the possibility that there are
positive or negative associations which shift the probability of
observing two species together due to their interaction (Cazelles
\emph{et al.} 2016). However, here we demonstrate that the probability
of observing a false negative can be higher if there is some positive
association in the occurrence of species \(A\) and \(B\).If we denote
the probability that we observe the co-occurrence of two species \(A\)
and \(B\) that we know interact as \(P(AB)\) and if there is no
association between the marginal probabilities of observing \(A\) and
observing \(B\), denoted \(P(A)\) and \(P(B)\) respectively, then the
probability of observing their co-occurrence \(P(AB) = P(A)P(B)\). In
the other case where there is some positive strength of association
between observing both \(A\) and \(B\) because this interaction is
``important'' for each species, then the probability of observation both
\(A\) and \(B\), \(P(AB)\), is greater than \(P(A)P(B)\) as \(P(A)\) and
\(P(B)\) are not independent and instead are positively correlated,
i.e.~\(P(AB)> P(A)P(B)\). In this case, the probability of observing a
false negative in our naive model from fig.~\ref{fig:geometric}(A) is
\(p_{fn}= 1-P(AB)\), which due to the above inequality implies
\(p_{fn} >1-P(A)P(B)\). This indicates an increasingly greater
probability of a false negative as \(P(AB) \to P(AB) \gg P(A)P(B)\).
However, this still does not consider variation in species abundancein
space and time (Poisot \emph{et al.} 2015). If positive or negative
associations between species structure variation in the distribution of
\(P(AB)\) across space/time, then the spatial/temporal biases induced by
data collection would further impact the realized false negative rate,
as the probability of false negative would not be constant for each pair
of species across sites.

@@

\begin{figure}
\hypertarget{fig:mangal}{%
\centering
\includegraphics{./figures/fig2.png}
\caption{The difference between joint-probability of co-occurrence
(P(AB)) and expected probability of co-occurrence under independence
(P(A)P(B)) for interacting species for each dataset. The red-dashed line
indicates 0. Each histogram represents a density, meaning the area of
the entire curve sums to 1. The continuous density estimate (computed
using local smoothing) is shown in grey. The p-value on each plot is the
result of a one-sided T-test comparing the mean of each distribution to
0.}\label{fig:mangal}
}
\end{figure}

@@

\begin{figure}
\hypertarget{fig:addedfnr}{%
\centering
\includegraphics{./figures/fig3.png}
\caption{(A) The area-under the receiver-operator curve (ROC-AUC). (B)
The area-under the precision-recall curve (PR-AUC; right) for each
different predictive model (colors/shapes) across a spectrum of the
proportion of added false negatives (x-axis). (C) The mean trophic-level
of all species in a network generated with the niche model across
different species richnesses (colors). For each value of the FNR, the
mean trophic level was computed across 50 replicates. The shaded region
for each line is one standard-deviation across those
replicates.}\label{fig:addedfnr}
}
\end{figure}

@@

@@

>>>>

\textbf{Correspondance to:}\\
Michael D. Catchen --- \texttt{michael.catchen@mcgill.ca}\\

@@

Species interactions drive many processes in evolutionary biology and
community ecology. A better understanding of interactions among species
is an imperative to both mitigate the potentially harmful impacts of
anthropogenic change on Earth's biodiversity (Makiola \emph{et al.}
2020) and to predict zoonotic spillover of disease to prevent future
pandemics (Becker \emph{et al.} 2021). However, meeting these challenges
is difficult because interactions are intrinsically hard to sample
(Jordano 2016). Over the past few decades biodiversity data has become
increasingly available---for example, remote-sensing has enabled
collection of data on spatial scales and resolutions previously
unimaginable (Stephenson 2020), while the adoption of open data
practices (Kenall \emph{et al.} 2014) have substantially increased the
amount of data available to ecologists. Still, widespread data about
species interactions remains elusive (Poisot \emph{et al.} 2021).
Observing an interaction between two species often requires human
observation because remote sampling methods can primarily detect
co-occurrence (but see Niedballa \emph{et al.} (2019)), and this itself
is not necessarily indicative of an interaction (Blanchet \emph{et al.}
2020). This constraint induces biases on species interaction data
subject to the spatial and temporal scales that current observation
methods can feasibly sample. This is further compounded by semantic
confusion around the word ``interaction''---for example one might
consider competition a type of species interaction, even though it is
marked by a lack of co-occurrence between species, unlike other types of
interactions, like trophism or pollination, which require both species
to be together at the same place and time. We define interaction in the
latter sense, where two species have fitness consequences on one-another
if they are in the sample place at the same time. In addition, here we
only consider direct (not higher-order) interactions.

The importance of \emph{sampling effort} and its impact on resulting
ecological data has produced a rich body of literature. The recorded
number of species in a dataset or sample depends on the total number of
observations (Walther \emph{et al.} 1995; Willott 2001)---as do
estimates of population abundance (Griffiths 1998)---in addition to
spatial coverage and species detectability. This has motivated more
quantitatively robust approaches to account for error in sampling data
in many contexts: to determine if a given species is extinct (Boakes
\emph{et al.} 2015), to determine sampling design (Moore \& McCarthy
2016),and to measure species richness across large scales (Carlson
\emph{et al.} 2020). In the context of interactions, an initial concern
was the compounding effects of limited sampling effort combined with the
amalgamation of data (across both study sites, time of year, and
taxonomic scales) could lead any empirical set of observations to
inadequately reflect the reality of how species interact (Paine 1988) or
the structure of the network as a whole (McLeod \emph{et al.} 2021).
Martinez \emph{et al.} (1999) showed that in a plant-endophyte trophic
network, network connectance is robust to sampling effort, but this was
done in the context of a system for which observation of 62,000 total
interactions derived from 164,000 plant-stems was feasible. In some
systems (e.g.~megafauna food-webs) this many observations is either
impractical or infeasible due to the absolute abundance of the species
in question.

We cannot feasibly observe all (or even most) of the direct interactions
that occur in an ecosystem. This means we can be confident two species
actually interact if we have a record of it (given an estimate of
species misidentification probability), but not at all confident that a
pair of species \emph{do not} interact if we have no record of those
species observed together. In other words, it is difficult to
distinguish \emph{true-negatives} (two species never interact) from
\emph{false-negatives} (two species interact sometimes, but we do not
have a record of it). For a concrete example of a false-negative in a
food web, see fig.~\ref{fig:concept}. Because even the most highly
sampled systems will still contain missing interactions, there is
increasing interest in combining species-level data (e.g.~traits,
abundance, range, phylogenetic relatedness, etc.) to build models to
predict interactions between species we haven't observed together before
(Strydom \emph{et al.} 2021). However, the noise of false-negatives
could impact the efficacy of our predictive models and have practical
consequences for answering questions about interactions (de Aguiar
\emph{et al.} 2019). This data constraint is amplified as the
interaction data we have is geographically biased toward the usual
suspects (Poisot \emph{et al.} 2021). We therefore need a systematic
approach to assessing these biases in the observation process and the
consequences this has for our understanding of interaction networks.

The intrinsic properties of ecological communities create several
challenges for sampling: first, species are not observed with equal
probability---we are much more likely to observe a species of high
abundance than one of very low abundance (Poisot \emph{et al.} 2015).
Canard \emph{et al.} (2012) presents a null model of food-web structure
where species encounter one-another directly in proportion to each
species' relative-abundance. This assumes that there are no associations
in species co-occurrence due to an interaction (perhaps because this
interaction is ``important'' for both species; Cazelles \emph{et al.}
(2016)), but in this paper we later show increasing strength of
associations leads to increasing probability of false-negatives in
interaction data, and that these positive associations are rampant in
existing network data. Second, observed co-occurrence is often equated
with meaningful interaction strength, but this is not necessarily the
case (Blanchet \emph{et al.} 2020)---a true ``non-interaction'' would
require that neither of two species, regardless of whether they
co-occur, exhibit any meaningful effect on the fitness of the other. So,
although co-occurrence is not directly indicative of an interaction, it
is a precondition for an interaction. Therefore observations of
``non-interactions'' between pairs of species that are outside of the
union of both species ranges do not provide any information about that
interaction, i.e.~they should be excluded from consideration.

Here, we illustrate how our confidence that a pair of species we believe
to not interact highly depends on sampling effort, and suggest that
surveys of species interactions can benefit from simulation modeling of
detection probability. We demonstrate that the realized false-negative
rate of interactions is directly related to the relative abundance of
the species involved, and demonstrate how simulation can be used to
produce a null estimate of the false-negative rate as a function of
total sampling effort (the total count of all individuals of all species
seen). We show that positive associations in co-occurrence data can
increase realized probability of false-negatives, and demonstrate these
positive associations are ubiquitous in network datasets. We conclude by
recommending that the simulation of sampling effort and species
occurrence can and should be used to help design surveys of species
interaction diversity (Moore \& McCarthy 2016), and by advocating use of
null models like those presented here as a tool for both guiding design
of surveys of species interactions and for modeling detection error in
predictive models.

@@

We start with a naive model of interaction detection: we assume that
every interacting pair of species is incorrectly observed as
not-interacting with an independent and fixed probability, which we
denote pfn and subsequently refer to as the False-Negative Rate (FNR).
If we observe the same species not-interacting \(N\) times, then the
probability of a true-negative (denoted \(p_{tn}\)) is given by
\(p_{tn}=1-(p_{fn})^N\). This relation (the probability-mass-function of
geometric distribution, a special case of the negative-binomial
distribution) is shown in Figure 1(A) for varying values of \(p_{fn}\)
and illustrates a fundamental link between our ability to reliably say
an interaction doesn't exist---\(p_{tn}\)---and the number of times we
have observed a given species. In addition, note that also there is no
non-zero \(p_{fn}\) for which we can ever prove that an interaction does
not exist---no matter how many observations of non-interactions \(N\) we
have, \(p_{tn}<1\).

From fig.~\ref{fig:geometric}(A) it is clear that the more often we see
two species co-occurring, but not interacting, the more likely the
interaction is a true negative. This has several practical consequences:
first it means negatives taken outside the overlap of the range of each
species aren't informative. Second, we can use this relation to compute
the expected number of total observations needed to obtain a ``goal''
number of observations of a particular pair of species
(fig.~\ref{fig:geometric}(B)). As an example, if we hypothesize that
\(A\) and \(B\) do not interact, and we want to see species \(A\) and
\(B\) both co-occurring and not interacting 10 times to be confident
this is a true negative, then we need an expected 1000 observations of
all species if the relative abundances of \(A\) and \(B\) are both
\(0.1\).

@@

We now show that the realized FNR changes drastically with sampling
effort due to the intrinsic variation of the abundance of individuals of
each species within a community. We do this by simulating the process of
observation of species interactions, applied both to 243 empirical food
webs from the Mangal database (Banville \emph{et al.} 2021) and random
food-webs generated using the niche model (Williams \& Martinez 2000), a
simple generative model of food-web structure. Our neutral model of
observation assumes each observed species is drawn from the distribution
in proportion to each species' abundance at that place and time. The
abundance distribution of a community can be reasonably-well described
by a log-normal distribution (Volkov \emph{et al.} 2003). In addition to
the log-normal distribution, we also tested the case where the abundance
distribution is derived from power-law scaling \(Z^{(log(T_i)-1)}\)
where \(T_i\) is the trophic level of species \(i\) and \(Z\) is a
scaling coefficient (Savage \emph{et al.} 2004), which yields the same
qualitative behavior. The practical consequence of abundance
distributions spanning many orders of magnitude of abundance is that
observing two ``rare'' species interacting requires two low probability
events: observing two rare species at the same time.

@@

where the MAP estimate of \((\mu, \phi)\) applied to Mangal data from
(MacDonald \emph{et al.} 2020) is \((\mu=0.086, \phi=24.3)\). All
simulations were done with 500 independent replicates per unique number
of observations \(n\). All analyses presented here are done in Julia
v1.8 (Bezanson \emph{et al.} 2015) using both EcologicalNetworks.jl v0.5
and Mangal.jl v0.4 (Banville \emph{et al.} 2021) and are hosted at
(GITHUB\_LINK\_TODO). Note that the empirical data, for the reasons
described above, very likely already contains many false negatives,
we'll revisit this issue in the final section.

From fig.~\ref{fig:geometric}(C) it is evident that the number of
species considered in a study is inseparable from the false-negative
rate in that study, and this effect should be taken into account when
designing samples of ecological networks in the future. We see a similar
qualitative pattern in fig.~\ref{fig:geometric}(D) where the FNR drops
off quickly as a function of observation effort, mediated by total
richness. The practical consequence of the bottom row of Figure 1 is
whether the total number of observations of all species (the x-axis) for
the range of possible FNR we deem acceptable (the y-axis) is feasible.
This raises two points: first, empirical data on interactions are
subject to the practical limitations of funding and human-work hours,
and therefore existing data tend to fall on the order of hundreds or
thousands observations of individuals per site. Clear aggregation of
data on sampling effort has proven difficult to find and a meta-analysis
of network data and sampling effort seems both pertinent and necessary,
in addition to the effects of aggregation of interactions across
taxonomic scales (Gauzens \emph{et al.} 2013; Giacomuzzo \& Jordán
2021). This inherent limitation on in-situ sampling means we should
optimize where we sample across space so that for a given number of
samples, we obtain the maximum information possible. Second, what is
meant by ``acceptable'' FNR? This raises the question: does a shifting
FNR lead to rapid transitions in our ability inference and predictions
about the structure and dynamics of networks, or does it produce a
roughly linear decay in model efficacy? We explore this in the next
section.

@@

This model above doesn't consider the possibility that there are
positive or negative associations which shift the probability of
observing two species together due to their interaction (Cazelles
\emph{et al.} 2016). However, here we demonstrate that the probability
of observing a false negative can be higher if there is some positive
association in the occurrence of species \(A\) and \(B\). If we denote
the probability that we observe the co-occurrence of two species \(A\)
and \(B\) that we know interact as \(P(AB)\) and if there is no
association between the marginal probabilities of observing \(A\) and
observing \(B\), denoted \(P(A)\) and \(P(B)\) respectively, then the
probability of observing their co-occurrence \(P(AB) = P(A)P(B)\). In
the other case where there is some positive strength of association
between observing both \(A\) and \(B\) because this interaction is
``important'' for each species, then the probability of observation both
\(A\) and \(B\), \(P(AB)\), is greater than \(P(A)P(B)\) as \(P(A)\) and
\(P(B)\) are not independent and instead are positively correlated,
i.e.~\(P(AB)> P(A)P(B)\). In this case, the probability of observing a
false negative in our naive model from fig.~\ref{fig:geometric}(A) is
\(p_{fn}= 1-P(AB)\), which due to the above inequality implies
\(p_{fn} >1-P(A)P(B)\). This indicates an increasingly greater
probability of a false negative as \(P(AB) \to P(AB) \gg P(A)P(B)\).
However, this still does not consider variation in species abundance in
space and time (Poisot \emph{et al.} 2015). If positive or negative
associations between species structure variation in the distribution of
\(P(AB)\) across space/time, then the spatial/temporal biases induced by
data collection would further impact the realized false negative rate,
as the probability of false negative would not be constant for each pair
of species across sites.

@@

\begin{figure}
\hypertarget{fig:mangal}{%
\centering
\includegraphics{./figures/fig2.png}
\caption{The difference between joint-probability of co-occurrence
(\(P(AB)\)) and expected probability of co-occurrence under independence
(\(P(A)P(B)\)) for interacting species for each dataset. The red-dashed
line indicates 0. Each histogram represents a density, meaning the area
of the entire curve sums to 1. The continuous density estimate (computed
using local smoothing) is shown in grey. The p-value on each plot is the
result of a one-sided t-test comparing the mean of each distribution to
0.}\label{fig:mangal}
}
\end{figure}

@@

\begin{figure}
\hypertarget{fig:addedfnr}{%
\centering
\includegraphics{./figures/fig3.png}
\caption{(A) The area-under the receiver-operator curve (ROC-AUC) and
(B) The area-under the precision-recall curve (PR-AUC; right) for each
different predictive model (colors/shapes) across a spectrum of the
proportion of added false negatives (x-axis). (C) The mean trophic-level
of all species in a network generated with the niche model across
different species richnesses (colors). For each value of the FNR, the
mean trophic level was computed across 50 replicates. The shaded region
for each line is one standard-deviation across those
replicates.}\label{fig:addedfnr}
}
\end{figure}

@@

\leavevmode\vadjust pre{\hypertarget{ref-McLeod2021SamAsy}{}}%
McLeod, A., Leroux, S.J., Gravel, D., Chu, C., Cirtwill, A.R., Fortin,
M.-J., \emph{et al.} (2021).
\href{https://doi.org/10.1111/oik.08650}{Sampling and asymptotic network
properties of spatial multi-trophic networks}. \emph{Oikos}, 130,
2250--2259.

@@

\leavevmode\vadjust pre{\hypertarget{ref-Paine1988RoaMap}{}}%
Paine, R.T. (1988). \href{https://doi.org/10.2307/1941141}{Road Maps of
Interactions or Grist for Theoretical Development?} \emph{Ecology}, 69,
1648--1654.
